Unshuffling Permutations

### 2015-09-11 article.tex
reduction

  \begin{claim}
    \label{claim:no (nu'_1, nu'_1),(nu_3, nu_3),(sigma' ,sigma'),(nu_4, nu_4)-edge}
    There is
    neither a $(\nu'_1, \nu'_1)$-edge,
    nor a $(\nu_3, \nu_3)$-edge,
    nor a $(\sigma', \sigma')$-edge,
    nor a $(\nu_4, \nu_4)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu'_1, nu'_1),(nu_3, nu_3),(sigma' ,sigma'),(nu_4, nu_4)-edge}]
    Combine Claim~\ref{claim:one (nu_2, nu'_2)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:one (nu_3, nu'_3)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_3, \nu'_3)$-edge in $\mathcal{M}$.
    Combining Claim~\ref{claim:no (nu_1, nu_3)-edge no (nu'_1, nu_3)-edge},
    Claim~\ref{claim:no (nu'_1, nu'_1),(nu_3, nu_3),(sigma' ,sigma'),(nu_4, nu_4)-edge},
    Claim~\ref{claim:at most one (nu_2, nu_3)-edge},
    and Claim~\ref{claim:no (nu_3, nu'_2)-edge},
    we conclude that $N_3-1$ positions in $\nu_3$ are involved
    in edges of $\mathcal{M}$ that are
    neither ($\nu_1, \nu_3)$-edges,
    nor $(\nu_2, \nu_3)$-edges
    nor $(\nu'_1, \nu_3)$-edges
    nor $(\nu_3, \nu_3)$-edges.
    But $N_3 - 1 > 2N_4 + 2n + 2k + 4$ (the positions left) and hence
    $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis.
    \qed
  \end{proof}
  \begin{claim}
    \label{claim:no (sigma', nu_4)-edge}
    There is no $(\sigma', \nu_4)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (sigma', nu_4)-edge}]
    Combine Claim~\ref{claim:one (nu_3, nu'_3)-edge} with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

@@

@@

  \begin{proof}[of Claim~\ref{claim:one (nu_4, nu'_4)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_4, \nu'_4)$-edge in $\mathcal{M}$.
    \qed
  \end{proof}

>>>>

  \begin{claim}
    \label{claim:no edge below one (nu_2, nu_2)-edge}
    There is
    neither a $(\nu'_1, \nu'_1)$-edge,
    nor a $(\nu'_1, \nu_3)$-edge,
    nor a $(\nu'_1, \sigma')$-edge,
    nor a $(\nu'_1, \nu_4)$-edge
    nor a $(\nu_3, \nu_3)$-edge,
    nor a $(\nu_3, \sigma')$-edge,
    nor a $(\nu_3, \nu_4)$-edge,
    nor a $(\sigma', \sigma')$-edge,
    nor a $(\sigma', \nu_4)$-edge,
    nor a $(\nu_4, \nu_4)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no edge below one (nu_2, nu_2)-edge}]
    Combine Claim~\ref{claim:one (nu_2, nu'_2)-edge} together with the fact that
    $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

  The next two claims state that $\mathcal{M}$ actually contains
  all $(\nu_1, \nu'_1)$-edges and all $(\nu_2, \nu'_2)$-edges.

  \begin{claim}
    \label{claim: all (nu_1, nu'_1)-edges}
    $\mathcal{M}$ contains $N_1$ pairwise crossing $(\nu_1, \nu'_1)$-edges.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim: all (nu_1, nu'_1)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_1$ $(\nu_1, \nu'_1)$-edge.
    Combing Claim~\ref{claim:no (nu_2, nu'_1)-edge} and
    Claim~\ref{claim:no edge below one (nu_2, nu_2)-edge},
    we conclude that there exists a position $a$ in $\nu'_1$ that is
    involded in an edge $(a, a')$ in $\mathcal{M}$ that is
    neither a $\nu_1, \nu'_1)$-edge,
    nor a $(\nu_2, \nu'_1)$-edge,
    nor a $(\nu'_1, \nu'_1)$-edge.
    (In other words, $a' > 2N_1 + N_2$.)
    Furthermore, according to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim: all (nu_2, nu'_2)-edges}
    $\mathcal{M}$ contains $N_2$ pairwise crossing $(\nu_2, \nu'_2)$-edges.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim: all (nu_2, nu'_2)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_2$ $(\nu_2, \nu'_2)$-edge.
    Combing Claim~\ref{claim:no (nu_1, nu_2)-edge} and
    Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    we conclude that there exists a position $a$ in $\nu_2$ that is
    involded in an edge $(a, a')$ in $\mathcal{M}$ that is
    neither a $\nu_1, \nu_2)$-edge,
    nor a $(\nu_2, \nu_2)$-edge.
    Furthermore, according to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:one (nu_3, nu'_3)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_3, \nu'_3)$-edge in $\mathcal{M}$.
    Combining Claim~\ref{claim:no (nu_1, nu_3)-edge no (nu'_1, nu_3)-edge},
    Claim~\ref{claim:no edge below one (nu_2, nu_2)-edge},
    Claim~\ref{claim:at most one (nu_2, nu_3)-edge},
    and Claim~\ref{claim:no (nu_3, nu'_2)-edge},
    we conclude that $N_3-1$ positions in $\nu_3$ are involved
    in edges of $\mathcal{M}$ that are
    neither ($\nu_1, \nu_3)$-edges,
    nor $(\nu_2, \nu_3)$-edges
    nor $(\nu'_1, \nu_3)$-edges
    nor $(\nu_3, \nu_3)$-edges.
    But $N_3 - 1 > 2N_4 + 2n + 2k + 4$ (the positions left) and hence
    $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu_1, nu_4)-edge}
    There is no $(\nu_1, \nu_4)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_4)-edge}]
    Suppose, aiming at a contradiction, that there exists
    a $(\nu_1, \nu_4)$-edge $(a, b)$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(x, x')$
    in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have $x < a$.
    Therefore, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is incresing)
    and $\mu(x') > \mu(a')$ since $\nu'_1$ is above $\nu_4$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (nu_2, nu_4)-edge}
    There is no $(\nu_2, \nu_4)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_4)-edge}]
    Suppose, aiming at a contradiction, that there exists
    a $(\nu_2, \nu_4)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_3, nu'_3)-edge},
    there exists a $(\nu_3, \nu'_3)$-edge $(x, x')$
    in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have
    $x' < a'$.
    Therefore,
    we have $\mu(x) > \mu(a)$ (since $\nu_3$ is above $\nu_4$) and
    $\mu(x') < \nu(a')$ (since $\nu'_3$ is increasing),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{proof}[of Claim~\ref{claim:one (nu_4, nu'_4)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_4, \nu'_4)$-edge in $\mathcal{M}$.
    Combining
    Claim~\ref{claim:no (nu_1, nu_4), (nu'_1, nu_4)-edge}
    Claim~\ref{claim:no edge below one (nu_2, nu_2)-edge}
    Claim~\ref{}
    \qed
  \end{proof}

@@
